New approaches for boosting to uniformity

### 2014-09-29 assets/paperdraft/parts/metrics.tex
Make uniformity plots in paper style

\subsection{Advantages and Disadvantages of Different Metrics}
Let us compare two metrics that have proven most appropriate for our problem, SDE and Theil. We have some linearly spaced array of mass of particles
from interval $[0,1]$, some constant $\alpha$ linearly sapced in interval $[.1,1]$. The predictions are correlated with mass via beta distribution.
We have two distributions that are different in a way that they are symmetrical. SDE should show no changes if we flip the distribution, while the Theil should make difference between pit and peak. First distribution with a peak is given by:

@@

while the second one has minus sign in front.
\begin{figure}[H]
\centering
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/distribution1.png}
			\caption{Mass vs prediction}
		\end{subfigure}
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/efficiencies1.png}
			\caption{Efficiencies}
		\end{subfigure}
		\caption{Peak distribution}
\end{figure}

\begin{figure}[H]
\centering
	\includegraphics[width=8cm]{graphs/measures1.png}
	\caption{SDE and Theil}
\end{figure}

\begin{figure}[H]
\centering
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/distribution2.png}
			\caption{Mass vs prediction}
		\end{subfigure}
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/efficiencies2.png}
			\caption{Efficiencies}
		\end{subfigure}
		\caption{Pit distribution}
\end{figure}

\begin{figure}[H]
\centering
	\includegraphics[width=8cm]{graphs/measures2.png}
	\caption{SDE and Theil}
\end{figure}

@@

>>>>

\subsection{Advantages and Disadvantages of Different Metrics}
\subsubsection{Theil and SDE}
Let us compare two metrics that have proven most appropriate for our problem, SDE and Theil. We have some linearly spaced array of mass of particles
from interval $[0,1]$, some constant $\alpha$ linearly spaced in interval $[.1,1]$. The predictions are correlated with mass via beta distribution.
We have two distributions that are different in a way that they are symmetrical. SDE should show no changes if we flip the distribution, while the Theil should make difference between pit and peak. First distribution with a peak is given by:

@@

while the second one has minus sign in front. Figures~\ref{fig:peakdists}~and~\ref{fig:pitdists} show the distribution of the predictions
and classifier efficiency as a function of mass for the peak and pit distributions, respectively. 
\begin{figure}[H]
\label{fig:peakdists}
\centering
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/PeakDistributions.png}
			\caption{Mass vs prediction.}
		\end{subfigure}
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/PeakEffs.png}
			\caption{Mass vs efficiency. The different coloured lines correspond to
different global classifier efficiencies, as explained in the legend on the leftmost subplot.}
		\end{subfigure}
		\caption{Peak response distribution and efficiencies as a function of mass. }
\end{figure}

\begin{figure}[H]
\label{fig:pitdists}
\centering
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/PitDistributions.png}
			\caption{Mass vs prediction.}
		\end{subfigure}
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/PitEffs.png}
			\caption{Mass vs efficiency. The different coloured lines correspond to
different global classifier efficiencies, as explained in the legend on the leftmost subplot.}
		\end{subfigure}
		\caption{Pit response distribution and efficiencies as a function of mass.}
\end{figure}

\begin{figure}[H]
\centering
	\includegraphics[width=0.5\textwidth]{graphs/TheilVsMSE.png}
	\caption{Comparison of SDE and Theil uniformity measures for different values of the constant $\alpha$ for the peak and pit distributions.
The Theil can clearly distinguish between these two while the SDE measure cannot.}
\end{figure}

@@

\subsubsection{$D \to hhh$}
When our classifiers where applied to data set $D \to hhh$ we got uniformity measures for the SDE and Theil
metrics shown in Fig.~\ref{fig:d2hhhsdetheil}.
\begin{figure}[H]
\label{fig:d2hhhsdetheil}
\centering
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/D23hSignalEffs.png}
			\caption{Metrics for $D \to hhh$ signal.}
		\end{subfigure}
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/D23hBgEffs.png}
			\caption{Metrics for $D \to hhh$ background.}
		\end{subfigure}
		\caption{Uniformity metrics for the $D \to hhh$ data set. The (top) signal and (bottom) background uniformities are plotted as a function of the training stage of a given classifier, listed in the legends on the leftmost plots.}
\end{figure}

Both metrics shown similar results, and that there is no significant difference on real data sets.
The SDE and Theil metrics can be used together in limit cases to more precisely determine nature of a distribution.
